04_analysis

### 2023-05-31 04_analysis.Rmd
added violin and box plots

>>>>

Avg sound levels by band (scatterplot)
```{r}
avgdB <- TO_12 %>%
  summarize(TOL_25 = mean(TOL_25),
            TOL_31.5 = mean(TOL_31.5),
            TOL_40 = mean(TOL_40),
            TOL_50 = mean(TOL_50),
            TOL_63 = mean(TOL_63),
            TOL_80 = mean(TOL_80),
            TOL_100 = mean(TOL_100),
            TOL_125 = mean(TOL_125),
            TOL_160 = mean(TOL_160),
            TOL_200 = mean(TOL_200),
            TOL_250 = mean(TOL_250),
            TOL_315 = mean(TOL_315),
            TOL_400 = mean(TOL_400),
            TOL_500 = mean(TOL_500),
            TOL_630 = mean(TOL_630),
            TOL_800 = mean(TOL_800),
            TOL_1000 = mean(TOL_1000),
            TOL_1250 = mean(TOL_1250),
            TOL_1600 = mean(TOL_1600),
            TOL_2000 = mean(TOL_2000),
            TOL_2500 = mean(TOL_2500),
            TOL_3150 = mean(TOL_3150),
            TOL_4000 = mean(TOL_4000),
            TOL_5000 = mean(TOL_5000),
            TOL_6300 = mean(TOL_6300),
            TOL_8000 = mean(TOL_8000),
            TOL_10000 = mean(TOL_10000),
            TOL_12500 = mean(TOL_12500),
            TOL_16000 = mean(TOL_16000),
            TOL_20000 = mean(TOL_20000)) %>%
  pivot_longer(cols = TOL_25:TOL_20000,
               names_to = "frequency",
               values_to="dB")

ggplot(avgdB, aes(x = factor(frequency, levels = unique(frequency)), y = dB)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Box plots
```{r}
TO_longer <- pivot_longer(TO_14, cols = TOL_25:TOL_20000,
               names_to = "frequency",
               values_to="dB")
ggplot(TO_longer, aes(x = factor(frequency, levels = unique(frequency)), y = dB)) + 
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Violin plot
ggplot(TO_longer, aes(x = factor(frequency, levels = unique(frequency)), y = dB)) + 
  geom_violin() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
